### 2020-01-22 paper/conclusion.tex
After proofreading

\section{Conclusion} \label{Conclusion}
In the current work, we introduced design of reactivity control system for the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for the full-core geometry using 
SERPENT-2 Monte-Carlo code. We considered three various startup composition of 
the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and plutonium, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and transuranic vector, extracted from \gls{LWR} \gls{SNF}.

@@

Six different absorbing materials are considered in this work:
natural B$_4$C, B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
with transuranic vector from \gls{LWR}. The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

In case of malfunction of the other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failed to counteract the excess 
reactivity of the core initially loaded with reactor-grade Pu and transuranic 
(TRU) elements. However, the worth of the outer ring of the CSD is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

@@

The insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs positions. This shifts the neutron flux from the core center towards the periphery.

The integral and differential control rod worth are calculated for three 
different systems: all control rods, CSD, and SSD systems. The results show 
that all absorbing materials have almost the same integral rod worth in the 
upper half of the core. Further insertion of the control rods shows the unique 
absorption characteristics of each material.

@@

\section{Future work}
In Part II of this research effort, we will evaluate effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using 
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
simulation with taking into account the neutron precursors drift.

>>>>

\section{Conclusion} \label{Conclusion}
In the current work, we introduced design of a reactivity control system for the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). The 
design has been evaluated at the startup for the full-core geometry using 
SERPENT-2 Monte-Carlo code. We considered three various startup compositions of 
the fuel salt: (1) $^{232}$Th as fertile and $^{233}$U as fissile material; 
(2) $^{232}$Th and Pu, extracted from \gls{LWR} \gls{SNF}; (3) 
$^{232}$Th and TRU vector, extracted from \gls{LWR} \gls{SNF}.

@@

Six different absorbing materials are considered in this work:
natural B$_4$C, B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
with TRU vector from \gls{LWR}. The reason for this is the much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

In case of malfunction of the other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failed to counteract the excess 
reactivity of the core initially loaded with reactor-grade Pu and TRU elements.
However, the worth of the outer ring of the CSD is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

@@

The insertion of CRs deforms the radial flux shape in certain positions, i.e., around CRs. This shifts the neutron flux from the core center towards the periphery.

The integral and differential CR worth are calculated for three 
different systems: all CRs, CSD, and SSD systems. The results show 
that all absorbing materials have almost the same integral rod worth in the 
upper half of the core. Further insertion of the CRs shows the unique 
absorption characteristics of each material.

@@

\section{Future work}
In Part II of this research effort, we will evaluate the effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using a
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters' (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
simulation with taking into account the neutron precursors drift.

### 2020-01-22 paper/introduction.tex
After proofreading

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR systems, which was understudied and require further investigation. The 
unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. MSR designs have a drain tanks to 
hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), the MSR is commonly loaded with a larger amount of 
fuel than that required to achieve criticality (necessary for long-term core 
operation). This leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is large for many refueling scenarios 
\cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2020Strategies,ashraf2020whole}. 
The online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
to control the reactor is to insert or withdraw control rods made of material 
with a large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is a commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}. 
However, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the reactivity worth, and swelling limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and release 
almost no gas (absorbing neutrons mainly through (n,$\gamma$) reactions)
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}. However, reactivity control system for maneuvering and emergency shutdown was not introduced in the literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}. Therefore, the main objective of our study is to introduce a new 
fast reactivity control system based on control rods in the \gls{SD-TMSR} to control 
the reactivity during normal operation and shut down the reactor in case of 
emergency. Six different absorbing materials are 
applied to study the main neutronics and safety parameters in the SD-TMSR. We 
focus on the control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin of absorbing materials, and shadowing 
effects at steady state calculation.

>>>>

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2020whole,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR system, which was understudied and requires further investigation. The 
unique characteristics of the MSR (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have 
a negative total temperature coefficient of reactivity 
\cite{ashraf2020whole,robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,li_optimization_2018}.
Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. MSR designs have drain tanks to 
hold and cool down the liquid fuel in an emergency case. A freeze plug, which 
is located under the core, passively melts when the fuel temperature reaches a 
critical point, and drains the fuel salt from the reactor vessel to the drain 
tanks. The drain tanks have a subcritical
configuration with a large free 
surface area to readily dissipate heat by passive cooling 
\cite{elsheikh2013safety}.

At the Beginning of Life (BOL), the MSR is commonly loaded with a larger amount of 
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is large for many refueling scenarios 
\cite{ashraf2020Strategies,ashraf2020whole,rykhlevskii2019modeling,betzler2016modeling,ashraf2018nuclear,ashraf2019modeling}.
Additionally, during burnup, the online 
reprocessing and refueling leads to slow reactivity change, which 
should be compensated \cite{ashraf2020Strategies,ashraf2020whole}. 
The online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
to control the reactor is to insert or withdraw control rods made of material 
with a large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces an amount of negative reactivity into the 
core. This negative reactivity helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

Boron carbide (B$_4$C) is a commonly used material for the control rods 
\cite{zhong2019preliminary,steinbruck2010degradation,dunner1984absorber}; 
however, we may need to enrich the boron isotope ($^{10}$B) to reach 
the necessary absorption cross section. Additionally, issues related to helium gas release through (n,$\alpha$) reactions of $^{10}$B, high loss of the reactivity worth, and swelling limit the B$_4$C lifespan 
\cite{guo2019optimized}. Guo (2019), Gosset (2017), and Rudy (2011) summarized the properties of the 
potential alternative absorbers for Generation-IV reactors such as 
hafnium-based materials and rare earth element oxides. These absorbers have 
high thermal conductivity, good resistance to neutron irradiation, and
almost no gas release (absorbing neutrons mainly through (n,$\gamma$) reactions)
\cite{guo2019optimized,gosset2017absorber,konings2011comprehensive}.

The \gls{SD-TMSR} with a thermal power of 2,250 MW$_{th}$ 
\cite{ashraf2020whole,li_optimization_2018} is a graphite-moderated 
molten salt reactor. Adjusting fertile and fissile feed rates helps to control the reactivity of 
the SD-TMSR \cite{ashraf2020whole,ashraf2020Strategies,li_optimization_2018}. However, a reactivity control system for maneuvering and emergency shutdown has not been introduced in literature \cite{li_optimization_2018,zou2018transition,zhang2020radiotoxicity,jiang2012advanced,zou2018preliminary,ZOU2015114}. Therefore, the main objective of our study is to introduce a new 
fast reactivity control system based on control rods in the \gls{SD-TMSR} to control 
the reactivity during normal operation and shut down the reactor in case of 
emergency. Six different absorbing materials are 
applied to study the main neutronics and safety parameters in the SD-TMSR. We 
focus on the control rod design, absorption ability, integral and differential 
control rod worths, shutdown margin of absorbing materials, and shadowing 
effects at steady state calculation.
